Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-13 article/article.Rmd
Commit 2024-06-13 19:11

The main focus of this study is to investigate the time evolution of the CE events by
analyzing the GHI measurements at Thessaloniki. Cloud enhancements can be influenced
by different factors, such as the geometry, size and optical thickness of clouds,
their height in the atmosphere and on local weather regimes **!!!(ref)!!!**.  Some of
these factors are related to changes in climate; hence it would be reasonable to
expect capturing their contributions to the frequency of occurrence of CE events over
Thessaloniki, as well as to the average OIR and excess irradiation. 
The long-term trends were calculated using a first-order autoregressive model with the
'maximum likelihood' fitting method
[@Gardner1980; @Jones1980], by implementing the function 'arima' from the library
'stats' of the R programming language [@RCT2023]. All trends are reported together
with their $2\sigma$ error.

>>>>

The main focus of this study is to investigate the time evolution of the CE events by
analyzing the GHI measurements at Thessaloniki. Cloud enhancements can be influenced
by different factors, such as the geometry, size and optical thickness of clouds,
their height in the atmosphere and on local weather regimes [@Mol2023; @Veerman2022;
@Gristey2022; @Tzoumanikas2016].  Some of these factors are related to changes in
climate; hence it would be reasonable to expect capturing their contributions to the
frequency of occurrence of CE events over Thessaloniki, as well as to the average OIR
and excess irradiation.  The long-term trends were calculated using a first-order
autoregressive model with the 'maximum likelihood' fitting method [@Gardner1980;
@Jones1980], by implementing the function 'arima' from the library 'stats' of the R
programming language [@RCT2023]. All trends are reported together with their
$2\sigma$ error.
